Convergence of shearing rate $\omega_{\mathrm{E}\times\mathrm{B}}$ with boxsize in gradient driven simulation

### 2022-11-23 briefcommunicaton/briefcommunication.tex
#37: Fixed Plots, Started writing

%% Include graphic for two column with specific place, figrue* places graphic anywhere...
\newcommand{\includegraphicsTwoCol}[3]{
	\onecolumngrid
	\begin{center}
		\captionsetup{type=figure}
    	\includegraphics[width=\textwidth]{#1}
		\captionof{figure}{#2}
	\end{center}
	\twocolumngrid
	\label{#3}
	\increasecounter{fig}{2}
}

@@

%\title[Convergence of shearing rate $\omega_{\mathrm{E}\times\mathrm{B}}$ with boxsize]{
%	Convergence of shearing rate $\omega_{\mathrm{E}\times\mathrm{B}}$ with boxsize
%}

%\author{M. Lippert}
%	\altaffiliation{GitHub Repository for files reagarding this paper: \\ 
%					https://github.com/ManeLippert/Bachelorthesis-ZonalFlows}
%\author{F. Rath}
%	\altaffiliation{Author to whom correspondence should be addressed: \\ 
%					Florian.Rath1@uni-bayreuth.de}
%	\email{Florian.Rath1@uni-bayreuth.de}
%\author{A. G. Peeters}
%\affiliation{Physics Department, University of Bayreuth, 95440 Bayreuth, Germany}

@@

It is known that radially sheared zonal flows plays a significant role in nonlinear stabilization in tokamak plasmas. \cite{WACooper1988,doi:10.1063/1.859529,doi:10.1063/1.873896}. 
Through advection on the sheared zonal flows the turbulent structure in plasma gets deformed and tilted that causes an $E \times B$ nonlinearty. \cite{doi:10.1063/1.859529, doi:10.1063/1.871313, doi:10.1063/1.872367}
Zonal flows mediate spectral energy transfer to larger radial wave vectors. \cite{doi:10.1063/1.3033206, doi:10.1063/1.3675855, PhysRevLett.120.175002}
The strength of the shearing process is the $E \times B$ shearing rate $\omega_{\mathrm{E \times B}}$ which is the radial derivative of the advecting zonal flow velocity. \cite{doi:10.1063/1.871313, doi:10.1063/1.872847}
The shearing rate $\omega_{\mathrm{E \times B}}$ is defined as 
\begin{equation}
	\omega_{\mathrm{E \times B}} = \frac{1}{2} \frac{\partial^2 \langle \Phi \rangle}{\partial \psi^2}
	\label{eq:shearingrate}
\end{equation}
where $\langle \Phi \rangle$ is the zonal electrostatic potential and $\psi$ the radial coordinate that labels the flux surfaces. \cite{doi:10.1063/1.4952621, doi:10.1063/1.5035184, doi:10.1063/1.3005380}
It was shown that the nonlinear threshold for turbulence is directly related to shear stabilization. \cite{doi:10.1063/1.873896} 
Often the shear stabilization is expressed in the empirical Waltz rule $\omega_{\mathrm{E \times B}} \sim \gamma$, \cite{doi:10.1063/1.870934, doi:10.1063/1.872847} where $\gamma$ is defined as the maximum linear growth rate in the unstable mode. In the discovered zonal flows, also known as $E \times B$ staircase \cite{PhysRevE.82.025401}, exhibit amplitudes in terms of the $E \times B$ shearing rate satisfying the stabilization criteria. \cite{doi:10.1063/1.4952621, doi:10.1063/1.4961231}

\includegraphicsOneCol{Comparison/Boxsize/S6_rlt6.0_boxsize1x1-2x2-3x3_Ns16_Nvpar48_Nmu9_eflux_comparison.pdf}{Test}{fig:eflux}

%\includegraphicsOneCol{Comparison/Gradient-Length/S6_rlt6.0-6.3_boxsize1x1_Ns16_Nvpar64_Nmu9_eflux_comparison.pdf}{Test}{fig:eflux}

\includegraphicsOneCol{S6_rlt6.0/boxsize3x1/Ns16/Nvpar48/Nmu9/S6_rlt6.0_boxsize3x1_Ns16_Nvpar48_Nmu9_wexb_selection.pdf}{Test}{fig:eflux}

\includegraphicsOneCol{S6_rlt6.0/boxsize3x3/Ns16/Nvpar48/Nmu9/S6_rlt6.0_boxsize3x3_Ns16_Nvpar48_Nmu9_wexb_selection.pdf}{Test}{fig:eflux}

%\includegraphicsOneCol{Comparison/Gradient-Length/S6_rlt6.0-6.2_boxsize2x2_Ns16_Nvpar48-64_Nmu9_eflux_comparison.pdf}{Test}{fig:eflux}

\includegraphicsTwoCol{Comparison/Boxsize/S6_rlt6.0_boxsize2x1-2-3x1-3_Ns16_Nvpar48_Nmu9_eflux_comparison.pdf}{Test}{fig:test}

\includegraphicsTwoCol{Comparison/Boxsize/S6_rlt6.0_boxsize1-2-3-4x1_Ns16_Nvpar48_Nmu9_wexb_comparison.pdf}{Test}{fig:test}

%\includegraphicsTwoCol{Comparison/Boxsize/S6_rlt6.0_boxsize1-2-3-4x1_Ns16_Nvpar48_Nmu9_eflux_comparison.pdf}{Test}{fig:test}

\includegraphicsTwoCol{Comparison/Boxsize/S6_rlt6.0_boxsize1-2-3-4x1_Ns16_Nvpar48_Nmu9_comparison.pdf}{Test}{fig:test}

>>>>

%% Include graphic for two column with specific place, figrue* places graphic anywhere...
%\newcommand{\includegraphicsTwoCol}[3]{
%	\onecolumngrid
%	\begin{center}
%		\captionsetup{type=figure}
%    	\includegraphics[width=\textwidth]{#1}
%		\captionof{figure}{#2}
%	\end{center}
%	\twocolumngrid
%	\label{#3}
%	\increasecounter{fig}{2}
%}

\newcommand{\includegraphicsTwoCol}[3]{
	\begin{figure*}
    	\includegraphics[width=\textwidth]{#1}
		\caption{#2}
	\end{figure*}
	\label{#3}
	\increasecounter{fig}{2}
}

@@

%\title[Convergence of shearing rate $\omega_{\mathrm{E}\times\mathrm{B}}$ with boxsize in gradient driven simulation]{
%	Convergence of shearing rate $\omega_{\mathrm{E}\times\mathrm{B}}$ with boxsize in gradient driven simulation
%}

%\author{M. Lippert}
%	\altaffiliation{Repository of this work: \\ 
%					https://github.com/ManeLippert/Bachelorthesis-Shearingrate-Wavelength}
%\author{F. Rath}
%	\altaffiliation{Author to whom correspondence should be addressed: \\ 
%					Florian.Rath1@uni-bayreuth.de}
%	\email{Florian.Rath1@uni-bayreuth.de}
%\author{A. G. Peeters}
%\affiliation{Physics Department, University of Bayreuth, 95440 Bayreuth, Germany}

@@

\section{Introduction}
\label{sec:intro}

This brief communication focused on continuing the work Rath et. al \cite{doi:10.1063/1.4961231}. At the end Section IV it was 
discussed that the circumstances for which the staircase can fully develop are beyond the scope of the paper. To gain more
knowledge if the staircase can develop with the chosen box size from Ref 1.
This paper will focus on the effects of the box size on the E$\times$B staircase structure and if the wavelength converges with the box size.

%%% THEORY =================================================================================================================

\section{Theory}
\label{sec:theory}

It is known that radially sheared zonal flows plays a significant role in nonlinear stabilization in tokamak plasmas. \cite{WACooper1988,doi:10.1063/1.859529,doi:10.1063/1.873896}. 
Through advection on the sheared zonal flows the turbulent structure in plasma gets deformed and tilted that causes an E$\times$B nonlinearty. \cite{doi:10.1063/1.859529, doi:10.1063/1.871313, doi:10.1063/1.872367}
Zonal flows mediate spectral energy transfer to larger radial wave vectors. \cite{doi:10.1063/1.3033206, doi:10.1063/1.3675855, PhysRevLett.120.175002}
The strength of the shearing process is the E$\times$B shearing rate $\omega_{\mathrm{E \times B}}$ which is the radial derivative of the advecting zonal flow velocity. \cite{doi:10.1063/1.871313, doi:10.1063/1.872847}
The shearing rate $\omega_{\mathrm{E \times B}}$ is defined as 
\begin{equation}
	\omega_{\mathrm{E \times B}} = \frac{1}{2B} \frac{\partial^2 \langle \Phi \rangle}{\partial \psi^2}
	\label{eq:shearingrate}
\end{equation}
where $\langle \Phi \rangle$ is the zonal electrostatic potential and $\psi$ the radial coordinate that labels the flux surfaces. \cite{doi:10.1063/1.4952621, doi:10.1063/1.3005380}
It was shown that the nonlinear threshold for turbulence is directly related to shear stabilization. \cite{doi:10.1063/1.873896} 
Often the shear stabilization is expressed in the empirical Waltz rule $\omega_{\mathrm{E \times B}} \sim \gamma$, \cite{doi:10.1063/1.870934, doi:10.1063/1.872847} where $\gamma$ is defined as the maximum linear growth rate in the unstable mode. In the discovered zonal flows, also known as E$\times$B staircase \cite{PhysRevE.82.025401}, exhibit amplitudes in terms of the E$\times$B shearing rate satisfying the stabilization criteria. \cite{doi:10.1063/1.4952621, doi:10.1063/1.4961231}

\includegraphicsOneCol{Comparison/Boxsize/S6_rlt6.0_boxsize1x1-2x2-3x3_Ns16_Nvpar48_Nmu9_eflux_comparison.pdf}{
	Time traces of the heat conduction coefficient $\chi$ for $R/L_T = 6.0$ for radial and binormal increased boxsizes
}{fig:eflux-1x1-2x2-3x3-comparison}

\includegraphicsOneCol{S6_rlt6.0/boxsize3x1/Ns16/Nvpar48/Nmu9/S6_rlt6.0_boxsize3x1_Ns16_Nvpar48_Nmu9_wexb_selection.pdf}{
	Shearing rate $\omega_{\mathrm{ExB}}$ for different time intervals in which heat conduction is almost zero but staircase has not fully developed for boxsize 3$\times$1
}{fig:wexb-3x1-selection}

\includegraphicsOneCol{S6_rlt6.0/boxsize3x3/Ns16/Nvpar48/Nmu9/S6_rlt6.0_boxsize3x3_Ns16_Nvpar48_Nmu9_wexb_selection.pdf}{
	Stablized shearing rate $\omega_{\mathrm{ExB}}$ for boxsize 3$\times$3
}{fig:wexb-3x3-stable}

\includegraphicsTwoCol{Comparison/Boxsize/S6_rlt6.0_boxsize2x1-2-3x1-3_Ns16_Nvpar48_Nmu9_eflux_comparison.pdf}{
	Comparison of time traces of the heat conduction coefficient $\chi$ for $R/L_T = 6.0$ for boxsize 2$\times$1 compared to 2$\times$2 and 3$\times$1 compared to 3$\times$3
}{fig:eflux-2x1-2-3x1-3-comparison}

\includegraphicsTwoCol{Comparison/Boxsize/S6_rlt6.0_boxsize1-2-3-4x1_Ns16_Nvpar48_Nmu9_wexb_comparison.pdf}{
	Comparison of shearing rate $\omega_{\mathrm{ExB}}$ for radial increased boxsizes. The staircase structure got 
	shifted for better visibility.
}{fig:wexb-1-2-3-4x1-stable-comparison}

\includegraphicsTwoCol{Comparison/Boxsize/S6_rlt6.0_boxsize1-2-3-4x1_Ns16_Nvpar48_Nmu9_comparison.pdf}{
	\textbf{(a)} Time traces of the heat conduction coefficient $\chi$ for $R/L_T = 6.0$ for radial increased boxsizes \linebreak
	\textbf{(b)} Time traces of $\omega_{\mathrm{ExB}}^{\mathrm{max}}$ for radial increased boxsizes
}{fig:wexb-eflux-1-2-3-4x1-comparison}
